Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-08 Supplemental-Material-B-Annotated-Analysis.Rmd
Update Supplemental-Material-B-Annotated-Analysis.Rmd

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file 
lib <- c("rmarkdown", "knitr", "remedy", "bookdown", "psych",
         "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra",
         "sessioninfo", "tibble", "pander", "devtools",
         "data.table", "dplyr", "tidyr", "Hmisc", "kableExtra", 
         "stringr", "stringi", "reshape2", "lubridate")
invisible(lapply(lib, library, character.only = TRUE))  
rm(lib)

@@

>>>>

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file 
lib <- c("rmarkdown", "knitr", "remedy", "bookdown", "psych",
         "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra",
         "sessioninfo", "tibble", "pander", "devtools",
         "data.table", "plyr", "dplyr", "tidyr", "Hmisc", "kableExtra", 
         "stringr", "stringi", "reshape2", "lubridate")
invisible(lapply(lib, library, character.only = TRUE))  
rm(lib)

@@

```{r cleanWorker}
#  important names for Morning and Afternoon
  names.m <- c(
    "StartDate",
    "EndDate",
    "Finished",
    "Duration__in_seconds_",
    "RecordedDate",
    "ExternalReference",
    "Meta_Operating_System",
    "Contact_dum",
    "number",
    "time",
    "duration_1",
    "dyad.group",
    "gr_size",
    "gr_type_1",
    "gr_type_2",
    "gr_type_3",
    "gr_type_4",
    "gr_type_5",
    "gr_type_6",
    "gr_type_7",
    "gr_type_8",
    "gr_type_9",
    "gr_type_10",
    "gr_type_11",
    "gr_type_12",
    "gr_type_13",
    "gr_type_14",
    "gr_type_15",
    "gr_type_16",
    "gr_type_17_TEXT",
    "gr_context_1",
    "gr_context_2",
    "gr_context_3",
    "gr_context_4",
    "gr_context_5",
    "gr_context_6",
    "gr_context_7",
    "gr_context_8",
    "gr_context_9",
    "gr_context_10",
    "gr_context_11",
    "gr_context_12",
    "gr_context_13_TEXT",
    "gr_context_14_TEXT",
    "gr_dutchness",
    "dyad_type_1",
    "dyad_type_2",
    "dyad_type_3",
    "dyad_type_4",
    "dyad_type_5",
    "dyad_type_6",
    "dyad_type_7",
    "dyad_type_8",
    "dyad_type_9",
    "dyad_type_10",
    "dyad_type_11",
    "dyad_type_12",
    "dyad_type_13",
    "dyad_type_14",
    "dyad_type_15",
    "dyad_type_16",
    "dyad_type_17_TEXT",
    "Context_1",
    "Context_2",
    "Context_3",
    "Context_4",
    "Context_5",
    "Context_6",
    "Context_7",
    "Context_8",
    "Context_9",
    "Context_10",
    "Context_11",
    "Context_12",
    "Context_13_TEXT",
    "Context_14_TEXT",
    "keyMotive",
    "keymotive_fulfillemt_1",
    "keyMotive_Dutch_1",
    "autonomy_1",
    "competence_1",
    "relatedness_self_1",
    "relatedness_other_1",
    "qualityAccidental_1",
    "qualityVoluntary_1",
    "qualityCooperative_1",
    "qualityDutchy_1",
    "quality_overall_1",
    "quality_meaning_1",
    "quality_star_1",
    "wantInt",
    "desire_type_1",
    "desire_type_2",
    "desire_type_3",
    "desire_type_4",
    "desire_type_5",
    "desire_type_6",
    "desire_type_7",
    "desire_type_8",
    "desire_type_9",
    "desire_type_10",
    "desire_type_11",
    "desire_type_12",
    "desire_type_13",
    "desire_type_14",
    "desire_type_15",
    "desire_type_16",
    "desire_type_17_TEXT",
    "desire_context_1",
    "desire_context_2",
    "desire_context_3",
    "desire_context_4",
    "desire_context_5",
    "desire_context_6",
    "desire_context_7",
    "desire_context_8",
    "desire_context_9",
    "desire_context_10",
    "desire_context_11",
    "desire_context_12",
    "desire_context_13_TEXT",
    "desire_context_14_TEXT",
    "Reason_nodesire",
    "keyMotive_noInt",
    "keyMotive_noInt_fulf_1",
    "autonomy_NoInt_1",
    "competence_NoInt_1",
    "relatedness_1_NoInt_1",
    "thermometerDutch_1",
    "thermometerDutchInt_2",
    "ExWB_1",
    "alertness1",
    "calmness1",
    "valence1",
    "alertness2",
    "calmness2",
    "valence2",
    "inNonDutch",
    "NonDutchNum",
    "NonDutchType_1",
    "NonDutchType_2",
    "NonDutchType_3",
    "NonDutchType_4",
    "NonDutchType_5",
    "NonDutchType_6",
    "NonDutchType_7",
    "NonDutchType_8",
    "NonDutchType_9",
    "NonDutchType_10",
    "NonDutchType_11",
    "NonDutchType_12",
    "NonDutchType_13",
    "NonDutchType_14",
    "NonDutchType_15_TEXT",
    "date",
    "time.0",
    "LocationLatitude",
    "LocationLongitude"
  )

  names.a <- c(names.m, "keyInteraction_1", "keyInteractionTime")

# Create reduced data sets for morning and afternoon
  dat.mo <- dtWorker$raw.morning[, names.m]
  dat.mo$daytime <- "morning"

  dat.af <- dtWorker$raw.afternoon[, names.a]
  dat.af$daytime <- "afternoon"

# merge morning and afternoon measurements with indicator [+ clean up]
  daily.dat <- rbind.fill(dat.mo, dat.af)
  daily.dat <- daily.dat[daily.dat$ExternalReference != 55951, ]
  dtWorker$daily <- daily.dat
  rm(dat.mo, dat.af, names.m, names.a, daily.dat)

# names for pre-measurement
  names.pre <- c(
    "Finished",
    "age",
    "Gender",
    "Living",
    "roommate_1",
    "roommate_2",
    "roommate_3",
    "nationality",
    "SecondNationality",
    "timeNL_1",
    "Reason_2",
    "Reason_5",
    "Reason_7",
    "Reason_8_TEXT",
    "DutchLang",
    "occupation_1",
    "occupation_2",
    "occupation_3",
    "occupation_4",
    "occupation_7",
    "CurrentEducation_1",
    "education_level",
    "EduLang_2",
    "RUG_faculty",
    "Study.0",
    "association",
    "DutchMeetNum",
    "DutchFriends_1",
    "assimilation",
    "separation",
    "integration",
    "marginalization",
    "VIA_heritage",
    "VIA_Dutch",
    "SSAS_surrounding",
    "SSAS_privat",
    "SSAS_public",
    "autonomy",
    "relatedness",
    "competence",
    "anxiety",
    "swl",
    "alertness",
    "calmness",
    "valence",
    "date",
    "time",
    "City",
    "ZIP",
    "id"
  )

# reduced data set for pre measurement
  dat.pre.red <- dtWorker$raw.pre[, names.pre]

# merge with daily data [+ clean up]
  df.pre <- merge(
    x = dtWorker$daily,
    y = dat.pre.red,
    by.x = "ExternalReference",
    by.y = "id",
    all = T
  )
  rm(names.pre)

# adjust duplicate names to fit to indicate daily or pre measurement  
  names(df.pre) <- gsub("[[:punct:]]x", ".daily", names(df.pre))
  names(df.pre) <- gsub("[[:punct:]]y", ".pre", names(df.pre))

# names for post measurement  
  names.post <- c(
    "ExternalReference",
    "assimilation",
    "separation",
    "integration",
    "marginalization",
    "VIA_heritage",
    "VIA_Dutch",
    "anxiety",
    "swl",
    "rosenberg",
    "social_support",
    "stress",
    "discrimination",
    "discrimination_month",
    "NLE_1month",
    "NLE_6month",
    "NLE_12month"
  )

# reduced data set for post-measurement  
  dat.post.red <- dtWorker$raw.post[, names.post]

# merge post measurement with pre- and daily data  
  df <- merge(
    x = df.pre,
    y = dat.post.red,
    by.x = "ExternalReference",
    by.y = "ExternalReference",
    all = T
  )

# adjust duplicate names to indicate pre or post  
  names(df) <- gsub("[[:punct:]]x", ".pre", names(df))
  names(df) <- gsub("[[:punct:]]y", ".post", names(df))

# add to list
  dtWorker$combined <- df

# create data frame with cleaned data
  df <- dtWorker$combined %>%
    filter(Finished.pre == 1,
           Finished.daily == 1,
           !is.na(ExternalReference))

# add running number as measurement ID within participants   
  df$measureID = rowidv(df, cols = c("ExternalReference"))

  dtWorker$clean <- df

# clean up
  rm(df.pre, names.post, dat.post.red, dat.pre.red, df)

# Export reduced Data
  #write.csv(dtWorker$clean, "data/processed/MT_clean-merged_07-05-2018.csv", row.names = F)
  #save(dtWorker$clean, file = "data/processed/MT_clean-merged_07-05-2018.RData")
```

```{r cleanStudents}

```{r cleanMedical}
